### 2016-08-28 paper.tex
Rearrange wake figs so RM2 come before RVAT
Change title to include 'hydrokinetic'
Add RVAT-Re-dep perf Re dep fig to text; closes #69

{\Large \textbf\newline{Experimental Study of a Reference Model Vertical-Axis
        Cross-Flow Turbine}} \newline % Insert author names,
% affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1}, Martin Wosnik\textsuperscript{1,*}, Budi
Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
NH, 03824, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories,
P.O. Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip

@@

The tendency of $C_P$ to continue increasing slightly could be an effect of flow
curvature---caused by the finite $c/R$---which imparts a ``virtual camber''
\cite{Migliore1980}, or can be thought of as producing a ``lead'' in angle of
attack since cambered airfoils have non-zero lift at zero angle of attack
\cite{Goude2012}. The residual weak $Re$-dependence of the RM2 compared to the
$Re$-independence of the higher $c/R$ UNH-RVAT could be due to this virtual
camber effect, since camber has been shown to cause earlier $Re$-convergence of
the CFT's geometric torque coefficient when calculated from static foil
coefficients given by a viscous panel method, whereas characteristics like
lift-to-drag ratio do not converge as strongly \cite{Bachant2016-Energies}.

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}

    \caption{{\bf Reynolds Number effects on performance.} Power and drag
    coefficient at $\lambda=3.1$ plotted versus turbine diameter and approximate
    average blade root chord Reynolds number.}

@@

>>>>

{\Large \textbf\newline{Experimental Study of a Reference Model
        Cross-Flow Hydrokinetic Turbine}} \newline % Insert author names,
% affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1}, Martin Wosnik\textsuperscript{1,*}, Budi
Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
NH, 03824, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories,
P.O. Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip

@@

The tendency of $C_P$ to continue increasing slightly could be an effect of flow
curvature---caused by the finite $c/R$---which imparts a ``virtual camber''
\cite{Migliore1980}, or can be thought of as producing a ``lead'' in angle of
attack since cambered airfoils have non-zero lift at zero angle of attack
\cite{Goude2012}. The residual weak $Re$-dependence of the RM2 compared to the
$Re$-independence of the higher $c/R$ UNH-RVAT, shown in
Fig.~\ref{fig:rvat-perf-re-dep}, could be due to this virtual camber effect,
since camber has been shown to cause earlier $Re$-convergence of the CFT's
geometric torque coefficient when calculated from static foil coefficients given
by a viscous panel method, whereas characteristics like lift-to-drag ratio do
not converge as strongly \cite{Bachant2016-Energies}.

\begin{figure}
    \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}

    \caption{{\bf RM2 Reynolds Number effects on performance.} Power (left) and
    drag (right) coefficient at $\lambda=3.1$ plotted versus turbine diameter
    and approximate average blade root chord Reynolds number.}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-perf_re_dep.eps}

    \caption{{\bf UNH-RVAT Reynolds Number effects on performance.} Power (left)
    and drag (right) coefficient at $\lambda=1.9$ plotted versus turbine
    diameter and approximate average blade chord Reynolds number. Taken from
    \cite{Bachant2016-Energies}.}

    \label{fig:rvat-perf-re-dep}
\end{figure}
